\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage[margin=0.25in]{geometry}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{calc}

\title{Jonas Wechsler}
\author{209 West 39th street\\Austin, Texas 78751\\jonaswechsler@gmail.com\\512-239-8620\\UT EID: jaw5426}
\date{}
\begin{document}

	\maketitle
	\begin{tabularx}{\textwidth - 20pt}{@{}l X l}
		\textbf{EDUCATION} & &\\
		2011 - 2015 & \textbf{Liberal Arts and Science Academy High School (LASA)} & Austin, Texas\\
		\\
		\textbf{WORK EXPERIENCE} & &\\
		2013 - Present & \textbf{University of Texas Austin, Dept. of Computer Science} & \\
		& \emph{Intern} & 4 hours/week \\
		& Worked under Professor Calvin Lin over the summer of 2013 researching cache architecture related to irregular memory accesses. Continued over the summer of 2014 alongside Kiran Tomlinson, researching patterns in memory access streams and running simulations relating to memory level parallelism. & 10 weeks/yr\\
		\\
		2013 - 2014 & \textbf{\emph{For Fear the Glass May Shatter}} & \\
		& \emph{Animator} & 2 hours/week \\
		& Created digital animation for an opera about quantum physics that was performed at the Vortex Theatre and at the Fusebox Festival, Austin, TX, April 2014. (\url{http://www.fuseboxfestival.com/2014-festival/for-fear-the-glass-may-shatter}) & 8 weeks/yr\\
		\\
		2012 & \textbf{University of Texas Austin, Dept. of Computer Science} & \\
		& \emph{Summer Intern} & 8 hours/week \\
		& Worked under Professor Calvin Lin alongside a team of high school developers developing Waterbear (\url{http://waterbearlang.com/}), a visual programming environment for use in undergraduate courses at UT. The code was open source HTML, CSS, and Javascript/JQuery, using Git for version control. & 10 weeks/yr\\
		\\
		\textbf{ACTIVITIES} & & \\
		$2012 - present$ & \textbf{Various martial arts}\\
		$2013 - present$ & \emph{Tukong Moosul} & 5 hours/week\\
		& & 45 weeks/yr\\
		$2012 - 2013$ & \emph{Tae Kwon Do} & 2 hours/week\\
		& & 44 weeks/yr\\
		\\ 
		$11^{th} - 12^{th}$ & \textbf{LASA High School Math Tutor} & 1 hour/week\\
		& Nominated by teachers to tutor other students in Algebra I through Linear Algebra and Multivariable Calculus. & 16 weeks/yr\\
		\\ 
		$11^{th} - 12^{th}$ & \textbf{LASA High School Computer Science Club} & 2 hours/week\\
		& \emph{Founder, Officer, and Tutor} & 16 weeks/yr\\
		& I give lectures and help fellow Computer Science students with their work. & \\
		\\
		$11^{th} - 12^{th}$ & \textbf{LASAUIL Practice Website} & 2 hours/week\\
		& \emph{Developer, Graphics Designer} & 20 weeks/yr\\
		& Developing the front-end of a Computer Science training website for beginning and advanced competitors. (\url{http://lasauil.herokuapp.com/}) & \\
		\\
	\end{tabularx}
	\newpage
	\vspace*{4 mm}
	\begin{tabularx}{\textwidth - 20pt}{l X l}
		\textbf{ACTIVITIES} & & \\
		$11^{th}$ & \textbf{LASA High School Computer Competition Club} & 1 hour/week\\
		&  \emph{Member and competitor} & 16 weeks/yr\\
		& Gave lectures and competed in district, regional, and national competitions. & \\
		\\
		$10^{th} - 12^{th}$ & \textbf{National Honor Society}& \\
		& $\qquad \bullet \enspace$ Volunteered at the Trail of Lights, patrolling and answering questions. & 9 hours\\
		& $\qquad \bullet \enspace$ Volunteered at the Blanton Art Museum as an exhibit docent. & 5 hours\\
		& $\qquad \bullet \enspace$ Volunteered at the Austin Wildflower Center doing landscaping work: planting, tilling, spreading gravel. & 4 hours\\
		\\
		\textbf{HONORS \& AWARDS} & & \\
		$12^{th}$ & \textbf{ $12^{th}$ National Merit Scholar, Commended }& \\
		$11^{th}$ & \textbf{ HSCTF placed 7th of 767 teams }& \\
		& $\qquad \bullet \enspace$ Team captain in High School CTF, a cooperative competition centered around hacking and algorithms. & \\
		&  \textbf{ USA Computing Olympiad Silver division}& \\
		& $\qquad \bullet \enspace$ Prompted for efficiency and accuracy of algorithms. & \\
		&  \textbf{ AP Scholar with Distinction Award} & \\
		&  \textbf{ 11th Trustees Award} & \\
		$10^{th}$ &  \textbf{ Accepted to National Honors Society}& \\
		&  \textbf{ Top 20\% National French Exam Level 3} & \\
		$9^{th}$ &  \textbf{ UIL State Team Competition 1st} & \\
		&  \textbf{ UIL Regional Team Competition 1st} & \\
		&  \textbf{ UIL District Team Competition 1st} & \\
		&  \textbf{ Viperwolf Invitational Individual 1st} & \\
		&  \textbf{ Viperwolf Invitational Team 1st} & \\
		\\
		\textbf{SKILLS \& TALENTS} & & \\
		& \textbf{Languages} & \\
		& 5 years of french study. & \\
		\\
		& \textbf{Martial Arts} & \\
		& Practice Tukong Moosul and formerly Taekwondo, with a heavy emphasis on discipline and tradition.& \\
		\\
		& \textbf{Coding} & \\
		& Fluent in Java, C++, Javascript, HTML, CSS, Node.js, and Bash. & \\
	\end{tabularx}
\end{document}

